Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
Add a=0.5 sentence to Table 4 caption
Small edits and trimming

\section{Experiments}\label{sec:experiments}
For our experiments we plan and execute queries for three separate survey-based data sets.
We show that \ProjectName{} performs an order of magnitude better than traditional
base-table imputation and produces results of comparable quality, showing that our system is well suited for early dataset exploration.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Runtimes for the queries in~\Cref{tbl:queries} using reference
    chained-equation decision trees algorithm. Using $\alpha=0$, \ProjectName{}
    is run at the highest quality setting, while with $\alpha=1$, performance
    is prioritized. Each query and each value of $\alpha$ was run 200 times.}
\label{fig:runtimes}
\end{figure}

@@

\textbf{Accuracy vs. Base-table Imputation (AVG)}\quad \Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results compared to the baseline, using the reference chained-equation decision trees model.
This measures the error introduced by on-the-fly imputation as compared to full imputation on the base tables.
This comparison is the relevant one in practice --- an analyst would only be considering the trade-offs in imputation quality and time in the first place for dirty input data, for which ground truth is unavailable.

@@

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations, as compared to the baseline.
Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). The count fraction column shows the number of tuples used in calculating each aggregate
     as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.}
\label{table:smape}
\end{table}

>>>>

usection{Experiments}\label{sec:experiments}
For our experiments we plan and execute queries for three separate survey-based data sets.
We show that \ProjectName{} performs an order of magnitude better than traditional
base-table imputation and produces results of comparable quality, showing that our system is well suited for early dataset exploration.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Runtimes for the queries in~\Cref{tbl:queries} using reference
    chained-equation decision trees algorithm, for various settings of $\alpha$.
    Each query and each value of $\alpha$ was run 200 times.}
\label{fig:runtimes}
\end{figure}

@@

\textbf{Accuracy vs. Base-table Imputation (AVG)}\quad \Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE) \cite{Makridakis2000451} for \ProjectName{}'s query results compared to the baseline, using the reference chained-equation decision trees model.
This measures the error introduced by dynamic imputation as compared to full imputation on the base tables.
This comparison is the relevant one in practice --- an analyst would only be considering the trade-offs in imputation quality and time in the first place for dirty input data, for which ground truth is unavailable.

@@

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations, as compared to the baseline.
Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). With ($\alpha=0.5$), an intermediate plan may be chosen if
    available.
    The count fraction column shows the number of tuples used in calculating each aggregate
     as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.}
\label{table:smape}
\end{table}
